### 2018-11-08 articleSFDS.tex
début corrections suites

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{ccccc}
    \rotatebox{90}{ \hspace{3em} \footnotesize $\mathcal{M}_2'$}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/eta.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/mu.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/ar.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/Serr.pdf}\\
	& $\eta$ & $\mu_t$ & $a_r$ & $\sigma_{err}^2$\\
	&&&&\\
    \rotatebox{90}{ \hspace{3em} \footnotesize $\mathcal{M}_4'$}
    &  \includegraphics[width=.2\textwidth]{figR/model4/after/densityEta.pdf}
    &  \includegraphics[width=.2\textwidth]{figR/model4/after/densityMu.pdf}
    &  \includegraphics[width=.2\textwidth]{figR/model4/after/densityAr.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densitySig.pdf}\\
		 & $\eta$ & $\mu_t$ & $a_r$ & $\sigma_{err}^2$\\
	&&&&\\
  \end{tabular}
\caption{Calibration results for $\mathcal{M}_2'$ and $\mathcal{M}_4'$ which uses the surrogate based on the sequential design.}
\label{fig:calibrationSeq}
\end{center}
\end{figure}

@@

The results of calibration performed for each model is displayed in Figure \ref{fig:calibrationSeq}. For each model, the \textit{prior} and the \textit{posterior} densities are confronted and in each case, it illustrates that a decrease of the variance which shows that calibration had improved the \textit{prior} knowledge. However the decrease of variance is not equal for every model. Indeed, in $\mathcal{M}_1$ the variances \textit{a posteriori} are lower than for $\mathcal{M}_2$. When the code is replaced by a surrogate based on a DOE of $50$ points, a term of variance is added (see equation (\ref{eq:VarianceFullLikelihood})) and the estimation is less accurate. The same phenomenon appears when comparing $\mathcal{M}_1$ and $\mathcal{M}_3$. The add of the discrepancy has brought a new term in the variance in the likelihood which increase the variance \textit{a posteriori}. The model $\mathcal{M}_4$ which combines a surrogate and a discrepancy has then a bigger variance \textit{a posteriori} than with the other models.

@@

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{cccc}
&  $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_4'$ \\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{new/Model3/Serr.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4/Sig.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densitySigD.pdf}\\
	&\multicolumn{3}{c}{$\sigma_{\boldsymbol{\delta}}^2$}\\
	&&&\\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{new/Model3/psi.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4/psi.pdf}
	&  \includegraphics[width=.2\textwidth]{figR/model4/after/densityPsiD.pdf}\\
	&\multicolumn{3}{c}{$\psi_{\boldsymbol{\delta}}$}\\
  \end{tabular}   
\caption{\textit{Prior} (in blue) and posterior (in red) densities of $\sigma_{\boldsymbol{\delta}}^2$ and $\psi_{\boldsymbol{\delta}}$ for $\mathcal{M}_3$, $\mathcal{M}_4$ and $\mathcal{M}_4'$.}
\label{fig:comparisionDensities2}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{ccccc}
    \rotatebox{90}{ \hspace{3em} \footnotesize $\mathcal{M}_2'$}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/eta.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/mu.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/ar.pdf}
    & \includegraphics[width=.2\textwidth]{new/Model2sd/Serr.pdf}\\
	& $\eta$ & $\mu_t$ & $a_r$ & $\sigma_{err}^2$\\
	&&&&\\
    \rotatebox{90}{ \hspace{3em} \footnotesize $\mathcal{M}_4'$}
    &  \includegraphics[width=.2\textwidth]{new/Model4sd/eta.pdf}
    &  \includegraphics[width=.2\textwidth]{new/Model4sd/mu.pdf}
    &  \includegraphics[width=.2\textwidth]{new/Model4sd/ar.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4sd/Serr.pdf}\\
		 & $\eta$ & $\mu_t$ & $a_r$ & $\sigma_{err}^2$\\
	&&&&\\
  \end{tabular}
\caption{Calibration results for $\mathcal{M}_2'$ and $\mathcal{M}_4'$ which uses the surrogate based on the sequential design.}
\label{fig:calibrationSeq}
\end{center}
\end{figure}

@@

The results of calibration performed for each model is displayed in Figure \ref{fig:calibrationSeq}. For each model, the \textit{prior} and the \textit{posterior} densities are confronted and in each case, it illustrates that a decrease of the variance which shows that calibration had improved the \textit{prior} knowledge. However the decrease of variance is not equal for every model. Indeed, in $\mathcal{M}_1$ the variances \textit{a posteriori} are lower than for $\mathcal{M}_2$. When the code is replaced by a surrogate based on a DOE of $50$ points, a term of variance is added (see equation (\ref{eq:VarianceFullLikelihood})) and the estimation is less accurate. The same phenomenon appears when comparing $\mathcal{M}_1$ and $\mathcal{M}_3$. The add of the discrepancy has brought a new term in the variance in the likelihood which increase the variance \textit{a posteriori}. The model $\mathcal{M}_4$ which combines a surrogate and a discrepancy has then a bigger variance \textit{a posteriori} than with the other models. The right column in Figure \ref{fig:comparisionDensities1} illustrates the \textit{prior} and \textit{posterior} of the variance of the white Gaussian noise. A strong disagreement appears in the model $\mathcal{M}_1$ because the \textit{posterior} mode of $\sigma_{err}^2$.

@@

\begin{figure}[htbp!]
\begin{center}
  \begin{tabular}{cccc}
&  $\mathcal{M}_3$ & $\mathcal{M}_4$ & $\mathcal{M}_4'$ \\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{new/Model3/Serr.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4/Sig.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4sd/Sig.pdf}\\
	&\multicolumn{3}{c}{$\sigma_{\boldsymbol{\delta}}^2$}\\
	&&&\\
    \rotatebox{90}{ \hspace{3em} \small density}
	&  \includegraphics[width=.2\textwidth]{new/Model3/psi.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4/psi.pdf}
	&  \includegraphics[width=.2\textwidth]{new/Model4sd/psi.pdf}\\
	&\multicolumn{3}{c}{$\psi_{\boldsymbol{\delta}}$}\\
  \end{tabular}   
\caption{\textit{Prior} (in blue) and posterior (in red) densities of $\sigma_{\boldsymbol{\delta}}^2$ and $\psi_{\boldsymbol{\delta}}$ for $\mathcal{M}_3$, $\mathcal{M}_4$ and $\mathcal{M}_4'$.}
\label{fig:comparisionDensities2}
\end{center}
\end{figure}
